---
title: "Introduction to Celmod"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Celmod)
```

## Overview
This workflow briefly outlines the main steps in using Celmod to create and apply a model for estimating cell type proportions from bulk data

### 1) Examine format of pre-loaded bulk data and proportion files
```{r}
bdat_initial[1:5,1:5]
classprops_initial[,1:5]
```

### 2) Train Celmod with initial files
```{r}
model1=train_model(bdat_initial,classprops_initial,numgenevec=3:10,crossval_times=5,seedval=1,method_type ="pearson",quantileval=0.9)
```

### 3) Run Celmod-trained model on an expression matrix - here, re-input the original training matrix as an example.
Note that for an actual run, the training, test, and holdout sets would be non-overlapping as far as possible
```{r}
out1=predict_estimates(model1,bdat_initial)
```

### 4) Examine output of predicted proportion files, with sixth parameter value:
```{r}
out1$proportions[[6]][,1:5]
```

### 5) As an example, plot predicted and actual proportions of cell type 1 with sixth parameter value:
```{r}
plot(classprops_initial[1,],out1$proportions[[6]][1,],pch=19,xlab="Actual proportion",ylab="Predicted proportion")
```
